The \dealii Library, Version 9.1

### 2019-05-15 9.1/paper.tex
fix changelist URL
add an entry

The major changes of this release are:
\begin{itemize}
\item Improved support for automatic and symbolic differentiation;
\item Full support for $hp$ adaptivity in parallel computations;
\item Interfaces to the HDF5 file format and libraries.
\item Significantly extended GPU support.
\item Four new tutorial programs step-61, step-62, step-63, step-64,
  as well as one new code gallery program.
\end{itemize}
These will all be discussed in more detail in the
following section. There are a number of other noteworthy changes in this release:
\begin{itemize}
\item A number of bug fixes and performance improvements to the
  matrix-free framework and related geometric multigrid solvers. In
  particular, the implementation of the Chebyshev iteration, an often
  used smoother in the matrix-free context, has been revised to reduce
  vector accesses. This speeds up matrix-free
  multigrid solvers by up to 10-15\% on geometries with affine
  (parallelogram and parallelpiped) cells, and up to
  5\% on geometries with cells bounded by curved edges and faces.
\item Various variants of geometric multigrid solvers and matrix-free
  implementations were run on up to 304,128 cores during the acceptance phase of
  the SuperMUC-NG supercomputer, verifying the scalability of our
  implementations. Some performance bottlenecks on distributed triangulation
  with more than 100k MPI ranks have been fixed.
\marginpar{Luca: Please expand}
\item ParsedConvergenceTable.
\item The \texttt{FE\_BernardiRaugel} class implements the
  non-standard Bernardi-Raugel (BR) element that can be used as one part of
  a stable velocity/pressure pair for the Stokes equation
  \cite{BR85}. The BR element can be seen as either an enriched
  version of the $Q_1^d$ element with added bubble functions on each
  edge (in 2d) or face (in 3d), or as a reduced version of the $Q_2^d$
  element. It addresses the fact that the $Q_1^d\times Q_0$
  combination is not inf-sup stable (requiring a larger velocity
  space), and that the $Q_2^d\times Q_1$ combination is stable but
  sub-optimal since the velocity space is too large relative to the
  pressure space to provide additional accuracy commensurate with the
  cost of the large number of velocity unknowns. The BR space is
  intermediate to the $Q_1^d$ and $Q_2^d$ spaces.

@@

This release of \dealii contains a number of large and significant changes
that will be discussed in the following sections. It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}{
in the file that lists all changes for this release}, see \cite{changes91}.
(The file is also linked to from the web site of each release as well as
the release announcement.)
\marginpar{check that URL works!}

@@

\marginpar{Update after the release}
The 9.1 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_0_and_9_1_0.html}
     {around 15 incompatible changes}; see \cite{changes91}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item TODO
\end{itemize}

>>>>

The major changes of this release are:
\begin{itemize}
\item Improved support for automatic and symbolic differentiation;
\item Full support for $hp$ adaptivity in parallel computations;
\item Interfaces to the HDF5 file format and libraries.
\item Significantly extended GPU support.
\item Parallel GMG:
  \begin{itemize}
  \item see \cite{ClevengerHeisterKanschatKronbichler2019}
  \item performance optimizations
    \item new features?
    \item largest runs now at XYZ (Kronbichler?)
    \end{itemize}
\item Four new tutorial programs step-61, step-62, step-63, step-64,
  as well as one new code gallery program.
\end{itemize}
These will all be discussed in more detail in the
following section. There are a number of other noteworthy changes in this release:
\begin{itemize}
\item A number of bug fixes and performance improvements to the
  matrix-free framework and related geometric multigrid solvers. In
  particular, the implementation of the Chebyshev iteration, an often
  used smoother in the matrix-free context, has been revised to reduce
  vector accesses. This speeds up matrix-free
  multigrid solvers by up to 10-15\% on geometries with affine
  (parallelogram and parallelpiped) cells, and up to
  5\% on geometries with cells bounded by curved edges and faces.
\item Various variants of geometric multigrid solvers and matrix-free
  implementations were run on up to 304,128 cores during the acceptance phase of
  the SuperMUC-NG supercomputer, verifying the scalability of our
  implementations. Some performance bottlenecks on distributed triangulation
  with more than 100k MPI ranks have been fixed.
\marginpar{Luca: Please expand}
\item ParsedConvergenceTable.
\item The \texttt{FE\_BernardiRaugel} class implements the
  non-standard Bernardi-Raugel (BR) element that can be used as one part of
  a stable velocity/pressure pair for the Stokes equation
  \cite{BR85}. The BR element can be seen as either an enriched
  version of the $Q_1^d$ element with added bubble functions on each
  edge (in 2d) or face (in 3d), or as a reduced version of the $Q_2^d$
  element. It addresses the fact that the $Q_1^d\times Q_0$
  combination is not inf-sup stable (requiring a larger velocity
  space), and that the $Q_2^d\times Q_1$ combination is stable but
  sub-optimal since the velocity space is too large relative to the
  pressure space to provide additional accuracy commensurate with the
  cost of the large number of velocity unknowns. The BR space is
  intermediate to the $Q_1^d$ and $Q_2^d$ spaces.

@@

This release of \dealii contains a number of large and significant changes
that will be discussed in the following sections. It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}{
in the file that lists all changes for this release}, see \cite{changes91}.
(The file is also linked to from the web site of each release as well as
the release announcement.)

@@

\marginpar{Update after the release}
The 9.1 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}
     {around 15 incompatible changes}; see \cite{changes91}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item TODO
\end{itemize}
